Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2018-05-06 hpmoon-asoco.tex
Commenting on the abstract
Please @fergunet take a look. I think it should be rewritten almost
completely. There's no issue, despite reviewer 1 asking for an
improvement of the abstract.

One of the most extended methods to deal with high-dimensional multi-objective optimization problems are the distributed co-evolutionary algorithms. In these methods each processor deals only with a part of the decision space, that is, the individuals belonging to the same sub-population (island) explore the same subset of decision variables. However, only decomposable problems could be strictly implemented in parallel this way. A new approach is presented here to deal with un-decomposable problems, the selective operator application: instead of sharing parts of individuals, each processor applies the variation operators to a specific subset of the whole individual. We have previously proved that extending the length of these subsets, and therefore, sharing some search space between islands, implies an improvement in the results. Specifically, in this paper, a new method to automatically adapt the size of the overlapping, or shared sections, of the individuals has been compared to other collaborative evolutionary techniques considering different number of islands, chromosome sizes and benchmarks. The analysis of the obtained experimental results, by using different metrics, shows that our approach can provide statistically significant improvements with respect to the base algorithm.  Results also show that the relation between the number of islands (subpopulations) and the length of the chromosome (number of decision variables) is also a relevant factor to determine the most efficient alternative to distribute the decision variables.

>>>>

  Real world optimization problems usually have many dimensions and
  several objectives. The high dimensionality requires exceptional
  computing power, and the fact that several dimensions have to be
  searched at the same time add additional difficulty.
% One of the most extended methods to deal with high-dimensional
% multi-objective optimization problems are the distributed
% co-evolutionary algorithms.
% ----------------- This sentence is meaningless. It should be
% substituted by other stating that co-evolutionary algorithms can
% deal with it for some reason
% Besides, we're no longer saying that they are co-evolutionary in the
% title, but "island-based selective operator application". This
% should go to the abstract too - JJ

  In these methods %which ones? coevolutionary or selective operator
                   %application? - JJ
  each processor deals only with a part of the decision
space, that is, the individuals belonging to the same sub-population,
which are called {\em islands} in this context, explore the same subset of decision variables. However, only
decomposable problems could be strictly implemented in parallel this
way. A new approach, which we call {\em selective operator application} is presented here to deal with un-decomposable
problems: % so we are saying that high-dimensional multi-objective
          % problems are a challenge, but we are presenting a solution
          % for non-decomposable problems. What's what? - JJ
instead of sharing parts
of individuals, each processor applies the variation operators to a
specific subset of the whole individual. % this solves... - JJ
We have previously proved
that extending the length of these subsets, and therefore, sharing
a part of the search space among islands, implies an improvement in the
results % which results? - JJ
but in this paper, a new method to automatically
adapt the size of the overlapping, or shared sections, of the
individuals has been compared to other collaborative evolutionary
techniques considering different number of islands, chromosome sizes
and benchmarks. The analysis of the obtained experimental results, by
using different metrics, shows that our approach can provide
statistically significant improvements with respect to the base
algorithm. % in high-dimensional multi-objective problems? - JJ
Results also show that the relation between the number of
islands (subpopulations) and the length of the chromosome (number of
decision variables) is also a relevant factor to determine the most
efficient alternative to distribute the decision variables.  % This
                                % solves a problem or challenge we
                                % hadn't stated. - JJ
